Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-21 automatica/paper.tex
response
Newer CBMC ref

\note{Ref to Fig. \ref{fig:digitalsystem} anywhere?}

@@

We employ the bounded model checker CBMC~\cite{ClarkeKL04} \note{newer reference?} to model the controller behavior on digital signals with finite bit-precision.  
We express the controller semantics as C programs, which is CBMC's preferable input language.  
CBMC symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem \note{merge this sentence with next?}.  
At the end of this process, the entire input program is translated to a boolean satisfiability formula which is satisfiable iff a certain property about the program holds.  
CBMC's API allows to specify these properties in the form of assertions in the input program: 
we set these properties to express that our controllers generate (asymptotically stable and) safe dynamics. 
%\note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
%etc. are turned into formulas? Part of Sec.~\ref{sec:errors} can probably be moved here.}

>>>>

\note{Ref to Fig. \ref{fig:digitalsystem} anywhere?. That figure is referred to in the section on errors. I think it is confusing to
refer to it before we have explained the DAC, ADC and the errors shown in the figure.}

@@

We employ the bounded model checker CBMC~\cite{DBLP:conf/tacas/KroeningT14} to model the controller behavior on digital signals with finite bit-precision.  
We express the controller semantics as C programs, which is CBMC's preferable input language.  
CBMC symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem \note{merge this sentence with next?}.  
At the end of this process, the entire input program is translated to a boolean satisfiability formula which is satisfiable iff a certain property about the program holds.  
CBMC's API allows to specify these properties in the form of assertions in the input program: 
we set these properties to express that our controllers generate (asymptotically stable and) safe dynamics. 
%\note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
%etc. are turned into formulas? Part of Sec.~\ref{sec:errors} can probably be moved here.}
